### 2019-12-19 defesa/tex/chapter/introducao.tex
wip

The second type of covering problems arose from the fact that covering almost all the demand set can be a lot cheaper than having to cover it all \cite{garcia}. This second type is known as \sigla{\MCLP}{Maximum Covering Location Problem}\footnote{Originally, the problem was defined using the word \textit{Maximal} on its title. In some sources, however, the word \textit{Maximum} is adopted.} and was introduced in \citeonline{church:1974}. In this first study, it is defined on a network with demand nodes, a facility set is also given and a solution maximizes the demand coverage satisfying the constraint that only a subset of the facilities is used. Just like the Minimum Cover, MCLP is a NP-Hard problem \cite{hatta:2013} and both deterministic, using integer programming in \citeonline{church:1974}, and heuristic methods in \citeonline{revelle:2008} have been proposed to solve it. A very complete survey of developments on this area can be found in \citeonline{mclp_review}.

In \citeonline{church:1984} a new kind of MCLP named \sigla{\PMCLP}{Planar Maximum Covering Location Problem} was introduced. Unlike its predecessor, this version of the problem was not defined on a network. Instead, on PMCLP the demand set and the facilities are located in $\R^2$ having a facility's coverage area be defined by a distance function. 
Initially, the Euclidean distance was considered and the idea behind the method proposed in \citeonline{church:1984} was to convert PMCLP into an instance of MCLP and then utilize any of the previous developed exact methods to obtain a solution for PMCLP. This reduction was done by identifying a \sigla{CLS}{Candidate Locations Set} which represented the possible locations that needed to be evaluated for every facility, so the optimal solution could be found. From the CLS, a network was built on which MCLP could be applied. Generating the CLS specifically for the case of Euclidean distance was done by the procedure called \sigla{CIPS}{Circle Intersect Points Set} which is described here on \autoref{chapter:pmclp}.

>>>>

The second type of covering problems arose from the fact that covering almost all the demand set can be a lot cheaper than having to cover it all \cite{garcia}. This second type is known as \sigla{\MCLP}{Maximum Covering Location Problem}\footnote{Originally, the problem was defined using the word \textit{Maximal} on its title. In some sources, however, the word \textit{Maximum} is adopted.} and was introduced in \citeonline{church:1974}. In this first study, it was defined on a network with demand nodes, a facility set is also given and a solution maximizes the demand coverage satisfying the constraint that only a subset of the facilities is used. Just like the Minimum Cover, MCLP is a NP-Hard problem \cite{hatta:2013} and both deterministic, using integer programming in \citeonline{church:1974}, and heuristic methods in \citeonline{revelle:2008} have been proposed to solve it. A very complete survey of developments on this area can be found in \citeonline{mclp_review}.

In \citeonline{church:1984} a new kind of MCLP named \sigla{\PMCLP}{Planar Maximum Covering Location Problem} was introduced. Unlike its predecessor, this version of the problem was not defined on a network. Instead, on PMCLP the demand set and the facilities are located in $\R^2$ having a facility's coverage area be defined by a distance function. 
Initially, the Euclidean distance was considered and the idea behind the method proposed in \citeonline{church:1984} was to convert PMCLP into an instance of MCLP and then utilize any of the previous developed exact methods to obtain a solution for PMCLP. This reduction was done by identifying a \sigla{CLS}{Candidate Locations Set} which represented the possible locations that needed to be evaluated for every facility, so the optimal solution could be found. From the CLS, a network was built on which MCLP could be applied. Generating the CLS specifically for the case of Euclidean distance was done by the procedure called \sigla{CIPS}{Circle Intersect Points Set} which will be described here on \autoref{chapter:pmclp}.
